Generalized spaces for constructive algebra

### 2020-04-09 paper-herrsching2019/main.tex
More references

Regarding spaces, the notion of locales can be modified in several ways.
Firstly, there are \emph{sites} and closely related
\emph{toposes}.~\cite{leinster:introduction,moerdijk-maclane:sheaves-logic}.
Given two opens~$U$ and~$V$ of a locale, there is only a truth value as to
whether~$U$ is contained in~$V$; with sites and toposes, there can be a
nontrivial \emph{set} of ways that~$U$ is contained in~$V$. In an orthogonal
direction, there is the notion of a \emph{formal
topology}~\cite{sambin:some-points,sambin:ifs}. These implement the idea of
pointfree topology in predicative settings.

@@

@@

@@

\begin{proof}Combination of Theorem~\ref{thm:basic-properties-sheaf-semantics}
and Corollary~\ref{cor:algebraic-reformulation}.\end{proof}

@@

% schuster:formal-zariski
% cls:spectral-schemes
really necessary? Wouldn't it suffice to define~$\Spec(A)$ as the topological
space of filters of~$A$? Indeed, for some time this was
believed~\cite[Section~3]{lawvere:icm-address}; however, this hope turned out
certain topos without any filters~\cite[pp.~200f.]{tierney:spectrum}, thus

XXX: Two views on A~
XXX: Direct definition of A~ possible

>>>>

Regarding spaces, the notion of locales can be modified in several ways.
Firstly, there are \emph{sites} and closely related
\emph{toposes}.~\cite{leinster:introduction,moerdijk-maclane:sheaves-logic}.
Given two opens~$U$ and~$V$ of a locale, there is only a truth value as to
whether~$U$ is contained in~$V$; with sites and toposes, there can be a
nontrivial \emph{set} of ways that~$U$ is contained in~$V$. In an orthogonal
direction, there is the notion of a \emph{formal
topology}~\cite{sambin:some-points,sambin:ifs}. These implement the idea of
pointfree topology in predicative settings. In this context also basics of
algebraic geometry have been
developed~\cite{schuster:formal-zariski,cls:spectral-schemes,cls:projective-spectrum}.

@@

\begin{remark}Given the importance of Theorem~\ref{thm:workhorse}, it is
natural to wonder where the proof stems from. Our proof proceeded in an ad hoc
fashion, verifying that the frame of radical ideals has the required properties
-- but where does the idea to use radical ideals come from? In general, determining the set
of provable sequents of a geometric theory is a challenging problem. Our most
efficient tool is probably the theory of \emph{entailment relations}. We refer
to Refs.~\refcite{rinaldi-schuster-wessel:edde,cederquist-coquand:entrel} and
the references therein and also strongly recommend the literature on dynamical
methods in commutative
algebra~\refcite{coste-lombardi-roy:dynamical-method,coquand-lombardi:logical-approach,coquand:site}.
\end{remark}

@@

The approach using locales and sheaves provides two ingredients which go beyond
mere syntax: Firstly, they give motivation for setting up the semantics in
the way we do (Section~\ref{sect:origins}). Secondly, they
conceptualize~$A^\sim$ as a single entity, just as rings like~$A/\mmm$
or~$A_\ppp$ are single entities; nevertheless, after unrolling the definitions,
any statement about~$A^\sim$ is merely a (logically more complex) statement
about~$A$ and its localizations~$A[f^{-1}]$.

@@

\begin{proof}Combination of Theorem~\ref{thm:basic-properties-sheaf-semantics}
and Corollary~\ref{cor:algebraic-reformulation}, or alternatively direct proof
by induction without using any preliminaries from earlier sections of this
contribution.\end{proof}

@@

FUTURE: Cite Duval and Joyal.
